---
title: "The QUACK Package: Tools for Quantification of Uncertainty and Calibration "
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(quack)
```



### 1. The Moment Penalization Prior

The Moment Penalization prior is a diagnostic tool for assessing overfitting in Bayesian models with random effects having a partially known distribution (usually Gaussian with fixed variance). Draws from this distribution can be obtained using the `rMP` function. 

```{R }
x <- rMP(300, p=2, w1=10, w2=10)
plot(x)
```

The density function can be evaluated using `dMP`. Since the normalization constant must be approximated with Monte Carlo (using `get_constMP`), the `normalized` boolean defaults to `FALSE` to avoid this computation. If `normalized = TRUE`, the number of MC replications can be set using the `MC` argument. 

```{R}
dMP(x[1,], w1=10, w2=10)
dMP(x[1,], w1=10, w2=10, normalized=TRUE) #Default MC=1e7
dMP(x[1,], w1=10, w2=10, normalized=TRUE, MC=1e6)
```

## 2. Local GP Emulators for Sequential Prediction: LEAP-GP and SLAP-GP

The `quack` package provides an implementation of the LEAP and SLAP GP emulators, which are modifications of the LA-GP framework which are more efficient for sequential prediction (i.e. settings where parallelization is not possible). For instance, we consider the `volcano` data which includes $5307$ obsrvations of the elevation of the Maunga Whau volcano, measured on a 10m by 10m grid. 

```{R, fig.height=6, fig.width=7}
X <- expand.grid(x1=seq(0,1,length.out=87), x2=seq(0,1,length.out=61))
y <- unlist(volcano)
XX <- expand.grid(x1=seq(0,1,length.out=20), x2=seq(0,1,length.out=20)) #Prediction set - not known in advance

leap <- leapGP_build(X, y)

#Prediction locations arrive in-situ
yhat1 <- rep(NA, 400)
for(i in 1:400){
  yhat1[i] <- leapGP_predict(leap, XX[i,])
}

#Combine LEAP and SLAP-GP
yhat2 <- rep(NA, 400)
leap <- leapGP_synch(leap, rho=0.95)
hubs <- leap$hubs
for(i in 1:400){
  slap <- slapGP(XX[i,], X, y, hubs=hubs)
  hubs <- slap$hubs
  yhat2[i] <- slap$pred
}

#Rearrange data
yhat1_mat <- yhat2_mat <- matrix(NA, nrow=20, ncol=20)
cnt <- 1
for(i in 1:20){
  for(j in 1:20){
    yhat1_mat[i,j] <- yhat1[cnt]
    yhat2_mat[i,j] <- yhat2[cnt]
    cnt <- cnt + 1
  }
}

#Make plots
par(mfrow=c(1,3))
contour(volcano, main="Volcano Data")
contour(t(yhat1_mat), main="LEAP-GP Predictions")
contour(t(yhat2_mat), main="SLAP-GP Predictions")
```


